|

### 2020-08-06 paper.Rmd
Diagram (Fig 2) updated.

```{r, out.width="30%", fig.cap="Diagram illustrating volume vs projected volume for a 3D sphere. The full sphere has volume $V(R, p)$. Within a radius $r$ the sphere contains the reduced volume $V(r; p, R)$, but the projected volume within a radius $r$ in a 2D plane is much larger, $V_{2D}(r; p ,R)$.", fig.align = "center"}

xp <- 0.1
n <- 200

@@

ggplot() +
  geom_circle(aes(x0= 0, y0=0, r = 1)) +
  geom_circle(aes(x0= 0, y0=0, r = xp)) +
  geom_ellipse(aes(x0 = 0, y0 = 0, a = 1, b = 0.2, angle = 0)) +
  geom_ellipse(aes(x0 = 0, y0 = 0, a = xp, b = xp/5, angle = 0)) +
  geom_area(aes(x=x, y=yp), fill = "red", alpha = 0.5) +
  geom_area(aes(x=x, y=ym), fill = "red", alpha = 0.5) +
  geom_segment(aes(x = 0, y = 0, xend = 1, yend = 0),
               size = 0.5, arrow = arrow(length = unit(0.1, "inches"))) +
  annotate("text", x = 0.5, y = 0.05, label="R") +
  geom_segment(aes(x = 0, y = 0, xend = xp, yend = 0),
               size = 0.5, arrow = arrow(length = unit(0.1, "inches"))) +
  annotate("text", x = xp/2, y = 0.05, label="r") +
  annotate("text", x = 0, y = 0.5, label=TeX("$V_{2D}(r; p, R)$")) + 
  annotate("text", x = -0.2, y = 0.05, label=TeX("$V(r; p, R)$")) + 
  annotate("text", x = 0.5, y = 0.25, label="V(R,p)") +
  theme_void() +
  coord_fixed()

>>>>

```{r, out.width="60%", fig.cap="The diagram on the left is illustrating the different volumes considered for a three-dimensional sphere. The full sphere has volume $V(R, p)$. Within a radius $r$ the sphere contains the reduced volume $V(r; p, R)$, shown in blue, but the projected volume within a radius $r$ in a two-dimensional plane is much larger, given by the volume of the cylinder with rounded caps, $V_{2D}(r; p ,R)$, shown in red. The intersection of the plane with the sphere is illustrated in grey, and the plane with both radii is shown in the right diagram.", fig.align = "center"}

xp <- 0.4
n <- 200

@@

p1 <- ggplot() +
  geom_ellipse(aes(x0 = 0, y0 = 0, a = 1, b = 0.2, angle = 0), fill = "grey") +
  geom_circle(aes(x0= 0, y0=0, r = 1)) +
  geom_circle(aes(x0= 0, y0=0, r = xp), color="red", fill = "blue", alpha=0.5) +
  geom_ellipse(aes(x0 = 0, y0 = 0, a = xp, b = xp/10, angle = 0), color="red") +
  geom_ellipse(aes(x0 = 0, y0 = sqrt(1 - (2*xp)^2/4)-xp/100, a = xp, b = xp/10, angle = 0), color="red") +
  geom_ellipse(aes(x0 = 0, y0 = -sqrt(1 - (2*xp)^2/4)+xp/100, a = xp, b = xp/10, angle = 0), color="red") +
  geom_area(aes(x=x, y=yp), fill = "red", alpha = 0.5) +
  geom_area(aes(x=x, y=ym), fill = "red", alpha = 0.5) +
  geom_segment(aes(x = 0, y = 0, xend = 1, yend = 0),
               size = 0.5, arrow = arrow(length = unit(0.1, "inches"))) +
  annotate("text", x = 0.5, y = 0.05, label="R") +
  geom_segment(aes(x = 0, y = 0, xend = 0, yend = xp),
               size = 0.5, arrow = arrow(length = unit(0.1, "inches"))) +
  annotate("text", x = -0.05, y = xp/2, label="r") +
  annotate("text", x = 0, y = 0.75, label=TeX("$V_{2D}(r; p, R)$")) + 
  annotate("text", x = 0, y = -xp * 0.75, label=TeX("$V(r; p, R)$")) + 
  annotate("text", x = 0.65, y = 0.5, label="V(R,p)") +
  theme_void() +
  coord_fixed()

p2 <- ggplot() +
  geom_circle(aes(x0= 0, y0=0, r = 1), fill = "grey") +
  geom_segment(aes(x = 0, y = 0, xend = 1, yend = 0),
               size = 0.5, arrow = arrow(length = unit(0.1, "inches"))) +
  annotate("text", x = 0.5, y = 0.05, label="R") +
  geom_segment(aes(x = 0, y = 0, xend = 0, yend = xp),
               size = 0.5, arrow = arrow(length = unit(0.1, "inches"))) +
  annotate("text", x = -0.05, y = xp/2, label="r") +
  geom_circle(aes(x0= 0, y0=0, r = xp), color="red") +
  theme_void() +
  coord_fixed()

grid.arrange(p1, p2, nrow=1)
